Temporal Distinctiveness in Task Switching: Assessing the Mixture-Distribution Assumption

### 2015-11-05 2015/Temporal Distinctiveness & Mixture Distributions/Manuscript Files/main.tex
final (ready for submission)

When RCI-ratio is high, so too is TD, which means there is a high probability the episodic trace can be retrieved; successful retrieval primes performance, leading to a fast RT. When the RCI-ratio is low, so too is TD, which lowers the probability of successful retrieval. When retrieval fails, the task must be performed via a slower, algorithmic route, leading to a slower RT \citep[see][for a similar proposal]{Logan2001}. Intermediate RCI-ratios lead to intermediate levels of TD; therefore, a proportion of these trials will have successful retrieval, and some trials will have failed retrieval.

@@

In the model, mean RT for a given trial is predicted by

@@

The previous section provided statistical support for the presence of a mixture-distribution for intermediate RCI ratios (i.e., intermediate levels of temporal distinctiveness). This is in agreement both with the verbal theory regarding TD effects \cite{Horoufchin2011a} and its formal implementation \cite{Grange2015}, which explains performance across RCI-ratios. In this section I develop a mathematical process model to predict RT distributions of RCI-ratio data. The fitting of whole RT distributions presents an important advance over the model of \citet{Grange2015}, as it allows a direct test---rather than a relatively indirect test from fitting mean RTs---of that model's core assumption: that intermediate TD performance is a weighted mixture of ``retrieved'' and ``not-retrieved'' processing modes, which lead to fast and slow RTs, respectively.

>>>>

When RCI-ratio is high, so too is TD, which means there is a high probability the episodic trace can be retrieved; successful retrieval primes performance, leading to a fast RT. When the RCI-ratio is low, so too is TD, which lowers the probability of successful retrieval. When retrieval fails, the task must be performed via a slower, algorithmic route, leading to a slower RT \citep[see][for a similar proposal]{Logan2002}. Intermediate RCI-ratios lead to intermediate levels of TD; therefore, a proportion of these trials will have successful retrieval, and some trials will have failed retrieval.

@@

In the model, mean RT for a given RCI-ratio is predicted by

@@

The previous section provided statistical support for the presence of a mixture-distribution for intermediate RCI ratios (i.e., intermediate levels of temporal distinctiveness). This is in agreement both with the verbal theory regarding TD effects \citep{Horoufchin2011a} and its formal implementation \citep{Grange2015}, which explains performance across RCI-ratios. In this section I develop a mathematical process model to predict RT distributions of RCI-ratio data. The fitting of whole RT distributions presents an important advance over the model of \citet{Grange2015}, as it allows a direct test---rather than a relatively indirect test from fitting mean RTs---of that model's core assumption: that intermediate TD performance is a weighted mixture of ``retrieved'' and ``not-retrieved'' processing modes, which lead to fast and slow RTs, respectively.
